### 2019-02-01 manuscript.tex
Update manuscript.tex

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote
sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
KandNwak09, OdukAfol17} (to confirm) should also be recognized. This study takes both the dynamics of attitudes and intention of FGC
practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether
FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems
insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point.
reframed and may still need more works.}

@@

The main response variables in this study were woman's intention to cut their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model.  The main predictors were attitudes of FGC benefits and woman's FGC status.  In order to test other theories mentioned above, we also included woman's gender awareness and other socio demogramic variables (see below).

>>>>

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote
sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
KandNwak09, OdukAfol17} (to confirm) should also be recognized. Both convention theory and gender_human rights approaches centre on values of emphasize values of how FGC associates with identity.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether
FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems
insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point.
reframed and may still need more works.}

@@

\cf{to add modernization measurement}
The main response variables in this study were woman's intention to cut their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model.  The main predictors were attitudes of FGC benefits and woman's FGC status.  In order to test other theories mentioned above, we also included woman's gender awareness and other socio demogramic variables (see below).
